A sheaf--function dictionary for algebraic tori over local fields

### 2013-08-25 shanghai.tex
Fixed a reference in bib.

If we specialize Proposition~\ref{prop:wrK} to the case when 
$T = \Gm{K}$ then $T'' = \Res_{K'/K} \Gm{K'}$ and we see that the functor $\QC(\GN{T}'')\to \QC(\GN{T})$ is the geometrization and categorification of restriction of quasicharacters from $(K')^\times$ to $K^\times$:
\[
\begin{tikzcd}[column sep=60]
\Hom_{\text{qc}}((K')^\times, \EEx) \arrow{r}{\chi \mapsto \chi\vert_{K^\times}} &\Hom_{\text{qc}}(K^\times, \EEx).
\end{tikzcd}
\]

>>>>

If we specialize Proposition~\ref{prop:wrK} to the case when 
$T = \Gm{K}$ then we see how to geometrize and categorify the restriction of quasicharacters from $(K')^\times$ to $K^\times$.
